### 2012-11-28 inst/examples/policycosts/policycosts_writeup.Rmd
fixed dependson (negative indexing not supported on CRAN version of knitr?)

This can take a while, so we use explicit parallelization, 
``` {r  parallel}
require(snowfall)
sfInit(cpu=8, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

@@

``` {r simulate_policy, dependson=c(-1,-2,-3,-4,-5,-6)}
sims <- list(
  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed), 
  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed),
  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy$D, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed),
  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_increase_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_increase(apples["increase"]), seed=seed),
  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"]), seed=seed),
  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=quad_profit, penalty= none, seed=seed)
)
````

>>>>

This can take a while, so we use explicit parallelization, 
``` {r  parallel}
require(snowfall)
sfInit(cpu=2, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

@@

``` {r simulate_policy, dependson=c("L1", "L2", "free_increase", "free_decrease", "fixed", "quad_costs")}
sims <- list(
  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed), 
  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed),
  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy$D, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed),
  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_increase_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_increase(apples["increase"]), seed=seed),
  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"]), seed=seed),
  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=quad_profit, penalty= none, seed=seed)
)
````
